# Week 3 Project

## Cash McGregor 

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->
```{r}
library(DataComputing)
library(mosaicData)
names(CPS85)
names(NCHS)
```
# Plot 1
1. This graphic uses a scatter plot to illustrate its data. 

2. Wage, exper, sector, and married are used in this graphic.

3. exper is the x-axis variable for all of the faceted graphics, wage is the y-axis for all of the graphics, sector is used to facet the graphics into 8 different graphs, and married is used to distinguish cases in each of the graphics.

```{r}
ggplot(data = CPS85, aes(x = exper, y = wage, color = married)) + geom_point() + facet_wrap( ~ sector)

```





# Plot 2
1. This graphic uses a density plot as its mode of graphic.

2. Sex, density, pregnancy and BMI are used from the data table.

3. Sex is differentiated by color in this graphic. Density is expressed as the vertical(y) axis 


```{r}
ggplot(data = NCHS, aes(x = bmi)) + geom_density(aes(color = sex, fill=sex ), alpha=0.3) + facet_wrap(~ smoker)

```

# Diamonds
```{r}
library(ggplot2)
names(diamonds)
```

```{r}
diamonds %>% 
  group_by(color) %>% 
  summarise(msizecolor = mean(carat)) %>%
  arrange(desc( msizecolor )) %>%
  head( 1 )
```
1. Color J has the highest average weight of diamond.

```{r}
diamonds %>% 
  group_by(clarity)%>% 
  summarise(mtable = mean(table))%>% 
  arrange(desc( mtable )) %>% 
  head( 1 )

```
2. I1 has the largest table average among the clarities. 

# Voting
```{r}
names(Minneapolis2013)
```
1. 80101
```{r}
Minneapolis2013 %>%
  summarise(total = n())
```
2. Betsy Hodges, Don Samuels, Mark Andrew, undervote, Jackie Cherryhomes
```{r}
  tally(group_by(Minneapolis2013,Second),sort=TRUE)
```
3. 1st: 834 2nd: 10598 3rd: 19210
```{r}
tally(group_by(Minneapolis2013,First),sort=TRUE)
tally(group_by(Minneapolis2013,Second),sort=TRUE)
tally(group_by(Minneapolis2013,Third),sort=TRUE)
```
4. Mark Andrew, Don Samuels, Jackie Cherryhomes
```{r}
Betsy <- Minneapolis2013 %>%
  filter(First == "BETSY HODGES")

tally(group_by(Betsy, Second), sort=TRUE) 
```
5. P-6C
```{r}
Minneapolis2013 %>%
  group_by(Precinct) %>%
  summarise(Fraction = mean(First == "undervote")) %>%
  arrange(desc(Fraction)) %>%
  head(1)
```