# Week 3 Short Answer Questions

## Cash McGregor

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
library("manipulate", lib.loc="/usr/local/lib/R/site-library")
```
<!-- put your content after this line -->
5.1
```{r}
library(mosaicData)
barGraphHelper(CPS85)
```

```{r}
View(HappinessIndex)
```

5.2
```{r}
WorldMap(HappinessIndex,key = "country" , fill = "corruption")
```

6.5
States and Polling Organizations

6.6
D. Rectangle. Graphical attribute: color and text.

6.7
D. NYT poll probability for the Democratic candidate.

6.8
```{r}
Small <-
  NCHS %>%
  sample_n(size=5000)
```

```{r}
scatterGraphHelper(Small)
``` 
The frame is set by bmi and weight. The glyph used is a circle that can be one of two colors, depending on if the person is a smoker or not.

7.1
a. Mean()
b. Variable1 / Variable2
c. rank()
d. filter()
e. %>% datatable groupby(A,X)
f. datatable %>% groupby(A,B) %>% summarise(value = max(X))

7.4
a. The argumenet in group_by should not have quotes around it. 
b. summarise() should have an equals sign in the argument.
c. The two functions are separate from each other. They will use the name of Tmp to represent two different things.

7.5
a. group_by(BabyNames, sex)
b. filter(BabyNames, sex=="F")
c. BabyNames %>% group_by(sex) %>% filter(count > 20)
d. summarise(BabyNames, total = sum(count))
e. BabyNames %>% group_by(name,count)

7.7
a. Using the piping tool %>% while using the name of the data table inside of the functions' arguments.
b. The functions do not have a data table to pull from because the first operator is naming the product of the functions.
c. It uses a naming argument in the middle of the chain of command.
d. Piping tool is backwards, naming operator is backwards, and the data table is at the end of the command. 

7.11
a. sex, count, meanAge
b. diagnosis, count, meanAge
c. sex, diagnosis, count , meanAge
d. Age, diagnosis, count, meanAge
e. Age, count, meanAge

7.12
a. n()
b. names(datatable)
c. help(datatable)
d. load(package)
e. Datatable %>% group_by(variable1, variable2, ...)
f. datatable %>% group_by(variable) %>% summarise(name = sum(quantvariable))
