# Week 2 Project

## Cash McGregor

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

```{r}
download.file("http://tiny.cc/dcf/Library-small.rda", 
              dest="Library-small.rda")
load("Library-small.rda")
```

```{r}
  Bks%>%
  tally()
  
```
## The above command tells us the amount of cases present in the Bks data table.
```{r}
  Bks%>%
  names()
```
## The above command tells us the names of every variable used in the Bks data table.
```{r}
Inv %>%
  group_by(Current.Status) %>%
  tally()
```
## The above command creates groups of cases that have the same entry for the variable "Current.Status" and calculates the amount of cases each of those categorical variables has.
```{r}
Inv %>%
  group_by(Issued.Count) %>%
  tally()
```
## The above command creates groups of cases depending on the amount of times a book has been checked out. It counts the amount of times each case has been checked out.